%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass{beamer}
\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
%\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{latexsym,amsmath,amscd,amssymb,epsfig,verbatim}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usepackage{tikz-qtree}
\tikzset{level distance=50pt,
    sibling distance=7pt,
    every tree node/.style={align=center},}

\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{conjecture}{Conjecture}
%\newtheorem*{conjecture*}{Conjecture}

\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
\newtheorem{eg}[thm]{Example}

%\newtheorem{counterexample}[thm]{Counterexample}
\newtheorem{defn}[thm]{Definition}
%\newtheorem{claim}[thm]{Claim}
%\newtheorem{note}[thm]{Notation}
%\newtheorem{warning}[thm]{Warning}
%\newtheorem{variant}[thm]{Variant}
%\newtheorem{question}[thm]{Question}
%\newtheorem{construction}[thm]{Construction}
%\newtheorem{terminology}[thm]{Terminology}
%\newtheorem{convention}[thm]{Convention}

%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\nc{\newcommand}
\nc\on{\operatorname}
\nc\renc{\renewcommand}
\newcommand\ssec{\subsection}
\newcommand\sssec{\subsubsection}
\newcommand\BH{{\mathbb H}}
\newcommand\bO{{\mathbf O}}
\newcommand\CC{{\mathcal C}}
\newcommand\CH{{\mathcal H}}
\newcommand\BN{{\mathbb N}}
\newcommand\BC{{\mathbb C}}
\newcommand\BF{{\mathbb F}}
\newcommand\BR{{\mathbb R}}
\newcommand\BQ{{\mathbb Q}}
\newcommand\BP{{\mathbb P}}
\newcommand\BBZ{{\mathbb Z}}
\newcommand\uR{\underline{R}}
\newcommand\uZ{\underline{\BBZ}}
\newcommand\CF{{\mathcal F}}
\newcommand\uCF{\underline{{\mathcal F}}}
\newcommand\BZ{{\mathbb Z}}
\newcommand\BA{{\mathbb A}}
\newcommand\fa{{\mathfrak a}}
\newcommand\fp{{\mathfrak p}}
\newcommand\fq{{\mathfrak q}}
\newcommand\fm{{\mathfrak m}}
\newcommand\so{{\mathscr O}}
\newcommand\sg{{\mathscr G}}
\newcommand \sx{{\mathscr X}}

\newcommand\scm{{\mathscr M}}
\newcommand\scn{{\mathscr N}}
\newcommand\scf{{\mathscr F}}
\newcommand\scg{{\mathscr G}}
\newcommand\sco{{\mathscr O}}
\newcommand\sch{{\mathscr H}}
\newcommand\scl{{\mathscr L}}
\newcommand\sci{{\mathscr I}}

\newcommand{\id}{\mathrm{id}}
\newcommand\im{\text{im }}
\newcommand\coker{\text{coker}}
\newcommand \spec{\text{Spec }}
\newcommand \proj{\text{Proj }}
\newcommand \rspec{\textit{Spec }}
\newcommand \rproj{\textit{Proj }}
\newcommand{\gal}{\mathrm{Gal}}

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\DeclareMathOperator\di{Div}
\newcommand \depth{\text{depth }}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\sym}{Sym}

%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand{\halfcan}{L}
\DeclareMathOperator{\Supp}{Supp}
\DeclareMathOperator{\initial}{in}
\DeclareMathOperator{\gin}{gin}
\DeclareMathOperator{\Eff}{Eff}
\DeclareMathOperator{\sat}{sat}

\newcommand{\GL}{\operatorname{GL}}
\newcommand{\SL}{\operatorname{SL}}
\newcommand{\PGL}{\operatorname{PGL}}
\newcommand{\PSL}{\operatorname{PSL}}


\newcommand\Wider[2][3em]{%
\makebox[\linewidth][c]{%
  \begin{minipage}{\dimexpr\textwidth+#1\relax}
  \raggedright#2
  \end{minipage}%
  }%
}


\AtBeginSection[]{
	\begin{frame}{Outline of Talk}
		\tableofcontents[currentsection]
	\end{frame}
}

%\usepackage{beamerthemeshadow}

\mode<presentation>{}
\usetheme{CambridgeUS}
\usecolortheme{beaver}

%%%%%%%%%%%%   Title slide info  %%%%%%%%%%%%%
\title{Log Spin Canonical Rings}
\author{Aaron Landesman\inst{1}, Peter Ruhm\inst{2}, Robin Zhang\inst{3}}
 
\institute[] % (optional)
{
  \inst{1}
	Harvard University
	,
  \inst{2}
	Stanford University
  ,
  \inst{3}
	Stanford University
}

\begin{document}

%%%%%%%%%%%%  Title Frame  %%%%%%%%%%%%%%%%
\begin{frame}
	\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%   Modular Forms Section   %%%%%%%%%%%%%%%%%%%
\section{Modular Forms} 

\begin{frame}{Fuchsian Group}
%Consider rings of modular forms of Fuchsian groups.
%\pause

\begin{defn}
$\Gamma$ is a {\bf Fuchsian} group if it is a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations.
\end{defn}

\pause
\begin{itemize}
\item Suppose $\Gamma \backslash \BH$ has finite area. \\
\pause
\item Then $\Gamma \backslash \BH$ can be given the structure of an {\bf{orbifold}} by completing it with cusps.  
\end{itemize}
%In presentation describe orbifold as a generalization to reimann surfaces that allow fractional points.

\end{frame}

%% frame

\begin{frame}{Modular Forms}
Let $\Gamma$  be a Fuchsian group (e.g.~$\Gamma = \Gamma_0(N) \subset \SL_2(\BZ)$).

\pause
\begin{definition}
A \textbf{modular form} for $\Gamma$ of weight $k \in \BZ_{\geq 0}$ is a holomorphic function $f \colon \BH \to \BC$ such that

\begin{align*}
	&f(\gamma z) = (cz+d)^k f(z) &\text{ for all } \gamma \in \Gamma 
\end{align*}

\noindent
and such that the limit $\lim_{z \to *} f(z)$ exists for all cusps $*$.
\end{definition}

\pause
\begin{defn}
  Let $M_k(\Gamma)$ be the $\BC$-vector space of modular forms for $\Gamma$ of weight $k$.    
\end{defn}

\end{frame}

%% frame

\begin{frame}{Ring of Modular Forms}

\begin{definition}[Ring of Modular Forms]
\[
	M(\Gamma) := \bigoplus_{k \in \BZ_{\geq 0}} M_k(\Gamma)
\]
\end{definition}

\pause
\begin{example}
\[
	M(\SL_2(\BZ)) \cong \BC[E_4,E_6]
\]
\end{example}

\pause
\begin{theorem}[Wagreich]
$M(\Gamma)$ is generated by two elements if and only if 
\[
	\Gamma = \SL_2(\BZ), \Gamma_0(2), \text{or } \Gamma(2).
\]

\end{theorem}
\end{frame}

%% frame

\begin{frame}{Translation to Geometry (Kodaira--Spencer)}
\begin{block}{Modular Curves}
\begin{enumerate}
  \item $Y = [\BH / \Gamma]$
  \item $X = Y \cup \Delta = [\overline{\BH} / \Gamma]$
\end{enumerate}
\end{block}

\pause
\begin{block}{\textbf{Kodaira--Spencer}}
\begin{align*}
  M_k(\Gamma) &\cong H^0(X, \Omega^1(\Delta)^{\otimes \frac{k}{2}}) \\
	f(z) &\mapsto f(z)\, dz^{\otimes \frac{k}{2}}
\end{align*}
\end{block}

\pause
\begin{block}{\textbf{Log Spin Canonical Ring}}
\begin{align*}
  M(\Gamma) &\cong R_{X,\Delta} := \bigoplus_k H^0(X, \Omega^1(\Delta)^{\otimes \frac{k}{2}}) \\
\end{align*}
\end{block}

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Stacky Curves Section   %%%%%%%%%%%%%%%%%%%
\section{Stacky Curves}

\begin{frame}{Stacky Curves}
\begin{defn}
A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$
is the data of
	\begin{itemize}
		\item smooth proper connected scheme $X$ of dimension $1$ \\ 
		\item together with a finite number of closed points of $X$, $P_
			1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer 
			orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ \\ 
		\item The scheme $X$ associated to a stacky curve $\sx$ is 
			called the {\bf coarse space} of $\sx$.
	\end{itemize}
\end{defn}

\pause

Then, we describe divisors on $\sx$ by
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]

\end{frame}

%% frame

\begin{frame}{Divisors}
We can equip stacky curves with a log divisor $\Delta$.

\begin{defn}
Divisor $\Delta$ is a \textbf{log divisor} if it is a sum of distinct
points each with trivial stabilizer.

Let $\delta := \deg \Delta$ refer to its degree.
\end{defn}

\pause
\begin{defn}
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
\end{defn}

\pause
\begin{defn}
$\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$.
\end{defn}

\end{frame}

%% frame

\begin{frame}{Log Spin Canonical Rings}

\begin{defn}
If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\end{defn}

\pause
\begin{defn}
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a divisor, then we define

\[
	H^0(\sx, D) := H^0(X, \lfloor D \rfloor).
\]
\end{defn}

\pause
\begin{defn}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan).
\]
\end{defn}

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Main Result Section   %%%%%%%%%%%%%%%%%%%
\section{Main Result}

\begin{frame}{Previous Work}
In particular, we bound the degrees of generators and relations of
a log spin canonical ring. Let $\sx$ be a stacky curve with
signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. The application
of O'Dorney's work \cite[Chapter 5]{dorney:canonical} to log spin
canonical rings gives a weak bound in the case $g = 0$ in terms of
the least common multiples of the $e_i$'s. In their treatment of
log spin canonical rings, Voight and Zureick-Brown
\cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
\cdot \max(e_1, \ldots, e_r)$ and relation degrees by $12 \cdot \max
(e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
bounds we write here differ from those stated in Voight and Zureick-
Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because
their grading convention differs from ours by a factor of 2.

These bounds are far from tight and do not collectively
cover all cases in all genera. The main theorem of this paper
gives significantly tighter bounds for the log spin canonical ring
of any log spin curve.
\end{frame}

\begin{frame}{Main Result}
\begin{alertblock}{Log Spin Canonical Ring Definition}
The \textbf{log spin canonical ring} of a stacky curve is
\[
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
\]
\end{alertblock}

Our main result gives the following bound

\pause
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$.

Then the log spin canonical ring is generated as a $k$-algebra by 
elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
relations generated in degrees at most $2e$,
so long as $\sigma$ does not lie in a finite list of exceptional
cases.
\end{thm}

\end{frame}

%% frame

\begin{frame}{Main Idea}
Induction on adding points.

Induction on raising stabilizer order.

\end{frame}

%% frame

\begin{frame}{Adding Points}
Adding points.

\end{frame}

%% frame

\begin{frame}{Raising Stabilizer Order}
Raising stabilizer order.

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Inductive Section   %%%%%%%%%%%%%%%%%%%
\section{Inductive Lemmas} 

\begin{frame}{Inductive Lemmas}
Lemmas?

\end{frame}

%%%%%%%%%%%%%%%%%%%%   High Genus Section   %%%%%%%%%%%%%%%%%%%
\section{High Genus} 

\begin{frame}{High Genus}
Not sure this is necessary.

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Genus One Section   %%%%%%%%%%%%%%%%%%%
\section{Genus One} 

\begin{frame}{Genus One}
This too.

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Genus Zero Section   %%%%%%%%%%%%%%%%%%%
\section{Genus Zero} 

\begin{frame}{Genus Zero}
Maybe a short description.

\end{frame}

%%%%%%%%%%%%%%%%%%%%   Further Research Section   %%%%%%%%%%%%%%%%%%%
\section{Further Research} 

\begin{frame}{Further Research}
Some questions.

\end{frame}


\begin{frame}
\frametitle{Acknowledgments}
Ken Ono!
David Zureick-Brown!
Great math atmosphere!

\end{frame}

\end{document}





